---
title: "AOM Frequency Sweeps"
output: html_notebook
---

This is a collection of code used to run the AOM frequency sweep for the atom 
control project. Each file set will be broken in to the various chunks. 
Sets that have more than one file will all be within one chunk.

```{r library call, message = FALSE}
library("tidyverse")
```

## 20161104 Sweep Test

```{r 2016104 sweep test}
freq_frame <- tibble(frequency = numeric(), step = integer())

for (i in 0:400) {
  frequency_step <- 1e5 
  
  frequency <- 60e6 + i * frequency_step
  
  new_frame <- tibble(frequency = frequency, step = as.integer(c(1, rep(0, times = 9)))) 
  
  freq_frame <- rbind(freq_frame, new_frame)
}

# write_csv(freq_frame, "AOM_frequency_sweeps/Files/20161104_Frequency_Sweep.csv", col_names = FALSE)
```

## 20161115 Atom Control Sweep Delay Tests

These are files for a few different tests. The parameters under testing are:

* The delay between the end of the frequency sweep and ionization 
* The time in between sweeps 
* The starting point of the sweep

For all of these the laser power, atomic density, and offset field will be 
constant and at the max level.

### End of sweep delay

To test the effect of the end of a frequency sweep we will start with 1 second 
of large detuning for MOT recovery (+100 MHz from resonance). We will then go 
to a +30 MHz detuning and sit there for various delays: 

* No delay
* 10 ms 
* 20 ms
* 100 ms
* 1 s

```{r}
freq_frame_30_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 85e6, 
                    step = as.integer(1))

freq_frame_30_MHz <- rbind(freq_frame_30_MHz, new_frame)

#write_csv(freq_frame_30_MHz, "AOM_frequency_sweeps/Files/20161115_30MHz_No_Delay.csv", col_names = FALSE)
```

```{r}
freq_frame_30_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 85e6, 
                    step = as.integer(c(1, 0)))

freq_frame_30_MHz <- rbind(freq_frame_30_MHz, new_frame)

#write_csv(freq_frame_30_MHz, "AOM_frequency_sweeps/Files/20161115_30MHz_10_ms_delay.csv", col_names = FALSE)
```

```{r}
freq_frame_30_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 85e6, 
                    step = as.integer(c(1, 0, 0)))

freq_frame_30_MHz <- rbind(freq_frame_30_MHz, new_frame)

#write_csv(freq_frame_30_MHz, "AOM_frequency_sweeps/Files/20161115_30MHz_20_ms_delay.csv", col_names = FALSE)
```

```{r}
freq_frame_30_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 85e6, 
                    step = as.integer(c(1, rep(0, times = 10))))

freq_frame_30_MHz <- rbind(freq_frame_30_MHz, new_frame)

#write_csv(freq_frame_30_MHz, "AOM_frequency_sweeps/Files/20161115_30MHz_100_ms_delay.csv", col_names = FALSE)
```

```{r}
freq_frame_30_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 85e6, 
                    step = as.integer(c(1, rep(0, times = 100))))

freq_frame_30_MHz <- rbind(freq_frame_30_MHz, new_frame)

#write_csv(freq_frame_30_MHz, "AOM_frequency_sweeps/Files/20161115_30MHz_1000_ms_delay.csv", col_names = FALSE)
```

## 20161116 Sweep Delay Tests at different Target detunings

This will follow a similar style as the sweeps from 20161115, but now we are 
testing to see what the ions look like at different target frequencies as well 
as different delays.

```{r}
freq_frame_40_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 80e6, 
                    step = as.integer(1))

freq_frame_40_MHz <- rbind(freq_frame_40_MHz, new_frame)

#write_csv(freq_frame_40_MHz, "AOM_frequency_sweeps/Files/20161117_40MHz_no_delay.csv", col_names = FALSE)
```

```{r}
freq_frame_50_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 75e6, 
                    step = as.integer(1))

freq_frame_50_MHz <- rbind(freq_frame_50_MHz, new_frame)

#write_csv(freq_frame_50_MHz, "AOM_frequency_sweeps/Files/20161117_50MHz_no_delay.csv", col_names = FALSE)
```

```{r}
freq_frame_60_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 70e6, 
                    step = as.integer(1))

freq_frame_60_MHz <- rbind(freq_frame_60_MHz, new_frame)

#write_csv(freq_frame_60_MHz, "AOM_frequency_sweeps/Files/20161117_60MHz_no_delay.csv", col_names = FALSE)
```

```{r}
freq_frame_70_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 65e6, 
                    step = as.integer(1))

freq_frame_70_MHz <- rbind(freq_frame_70_MHz, new_frame)

#write_csv(freq_frame_70_MHz, "AOM_frequency_sweeps/Files/20161117_70MHz_no_delay.csv", col_names = FALSE)
```

```{r}
freq_frame_100_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 50e6, 
                    step = as.integer(1))

freq_frame_100_MHz <- rbind(freq_frame_100_MHz, new_frame)

#write_csv(freq_frame_100_MHz, "AOM_frequency_sweeps/Files/20161116_100MHz_no_delay.csv", col_names = FALSE)
```

## 20161122 Atom Control Sweeps

These are sweeps from starting frequencies of 70 MHz, 60 MHz, 50 MHz, 40 MHz, 
and 30 MHz to a target detuning of 30 MHz. All of these scans have a second 
of 100 MHz detuning to allow for the MOT to replenish. The scans go from the 
starting detuning to the target detuning in 1 MHz steps every 10 ms.

```{r}
freq_frame_70_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(65e6, 85e6, by = 5e5), 
                    step = as.integer(1))

freq_frame_70_MHz <- rbind(freq_frame_70_MHz, new_frame)

#write_csv(freq_frame_70_MHz, "AOM_frequency_sweeps/Files/20161120_70MHz_sweep.csv", col_names = FALSE)
```

```{r}
freq_frame_60_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(70e6, 85e6, by = 5e5), 
                    step = as.integer(1))

freq_frame_60_MHz <- rbind(freq_frame_60_MHz, new_frame)

#write_csv(freq_frame_60_MHz, "AOM_frequency_sweeps/Files/20161120_60MHz_sweep.csv", col_names = FALSE)
```

```{r}
freq_frame_50_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(75e6, 85e6, by = 5e5), 
                    step = as.integer(1))

freq_frame_50_MHz <- rbind(freq_frame_50_MHz, new_frame)

#write_csv(freq_frame_50_MHz, "AOM_frequency_sweeps/Files/20161120_50MHz_sweep.csv", col_names = FALSE)
```

```{r}
freq_frame_40_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(80e6, 85e6, by = 5e5), 
                    step = as.integer(1))

freq_frame_40_MHz <- rbind(freq_frame_40_MHz, new_frame)

#write_csv(freq_frame_40_MHz, "AOM_frequency_sweeps/Files/20161120_40MHz_sweep.csv", col_names = FALSE)
```

```{r}
freq_frame_30_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 85e6, 
                    step = as.integer(1))

freq_frame_30_MHz <- rbind(freq_frame_30_MHz, new_frame)

#write_csv(freq_frame_30_MHz, "AOM_frequency_sweeps/Files/20161120_30MHz_sweep.csv", col_names = FALSE)
```

## 20161129 Atom Control Freq Sweeps, 5 MHz and 10 MHz steps

These are the same frequency sweeps as those from 2016 11 22, but now they 
have step sizes of 5 MHz and 10 MHz between each frequency.

### 5 MHz Steps

```{r}
freq_frame_70_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(65e6, 85e6, by = 2.5e6), 
                    step = as.integer(1))

freq_frame_70_MHz <- rbind(freq_frame_70_MHz, new_frame)

#write_csv(freq_frame_70_MHz, "AOM_frequency_sweeps/Files/20161129_70MHz_sweep_5_MHz_step.csv", col_names = FALSE)
```

```{r}
freq_frame_60_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(70e6, 85e6, by = 2.5e6), 
                    step = as.integer(1))

freq_frame_60_MHz <- rbind(freq_frame_60_MHz, new_frame)

#write_csv(freq_frame_60_MHz, "AOM_frequency_sweeps/Files/20161129_60MHz_sweep_5_MHz_step.csv", col_names = FALSE)
```

```{r}
freq_frame_50_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(75e6, 85e6, by = 2.5e6), 
                    step = as.integer(1))

freq_frame_50_MHz <- rbind(freq_frame_50_MHz, new_frame)

#write_csv(freq_frame_50_MHz, "AOM_frequency_sweeps/Files/20161129_50MHz_sweep_5_MHz_step.csv", col_names = FALSE)
```

```{r}
freq_frame_40_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(80e6, 85e6, by = 2.5e6), 
                    step = as.integer(1))

freq_frame_40_MHz <- rbind(freq_frame_40_MHz, new_frame)

#write_csv(freq_frame_40_MHz, "AOM_frequency_sweeps/Files/20161129_40MHz_sweep_5_MHz_step.csv", col_names = FALSE)
```

### 10 MHz Steps

```{r}
freq_frame_70_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(65e6, 85e6, by = 5e6), 
                    step = as.integer(1))

freq_frame_70_MHz <- rbind(freq_frame_70_MHz, new_frame)

#write_csv(freq_frame_70_MHz, "AOM_frequency_sweeps/Files/20161129_70MHz_sweep_10_MHz_step.csv", col_names = FALSE)
```

```{r}
freq_frame_60_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(70e6, 85e6, by = 5e6), 
                    step = as.integer(1))

freq_frame_60_MHz <- rbind(freq_frame_60_MHz, new_frame)

#write_csv(freq_frame_60_MHz, "AOM_frequency_sweeps/Files/20161129_60MHz_sweep_10_MHz_step.csv", col_names = FALSE)
```

```{r}
freq_frame_50_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(75e6, 85e6, by = 5e6), 
                    step = as.integer(1))

freq_frame_50_MHz <- rbind(freq_frame_50_MHz, new_frame)

#write_csv(freq_frame_50_MHz, "AOM_frequency_sweeps/Files/20161129_50MHz_sweep_10_MHz_step.csv", col_names = FALSE)
```

```{r}
freq_frame_40_MHz <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = seq(80e6, 85e6, by = 5e6), 
                    step = as.integer(1))

freq_frame_40_MHz <- rbind(freq_frame_40_MHz, new_frame)

#write_csv(freq_frame_40_MHz, "AOM_frequency_sweeps/Files/20161129_40MHz_sweep_10_MHz_step.csv", col_names = FALSE)
```

## 2016 12 07 Max Power Location

```{r}
freq_frame <- tibble(frequency = 50e6, 
                            step = as.integer(c(1, rep(0, times = 99))))

new_frame <- tibble(frequency = 82e6, 
                    step = as.integer(1))

freq_frame <- rbind(freq_frame, new_frame)

#write_csv(freq_frame, "AOM_frequency_sweeps/Files/20161207_Max_Power_Single_Shot.csv", col_names = FALSE)
```
